---
title: "MATH 3070 Lab Project 2"
author: "Max Martin"
date: "September 1, 2021"
output:
  pdf_document:
    toc: true
  html_document:
    toc: true
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 1.7)
*The `rivers` (**UsingR**) or any other data set is available after loading the package **UsingR**. Load the package, and inspect the data set. Scan the values to find the largest one.*

```{r}
# This is the command to load the UsingR package.
library(UsingR)
# This function iterates through the dataset to find the largest value, which is 3170 based on my own eye
# scanning and then of course the following function.
max(rivers)
```

## Problem 2 (Verzani problem 2.4)
*Create the following sequences, using `:`, `seq()`, or `rep()` as appropriate:*

1. `"a" "a" "a" "a" "a" "a"`

```{r}
# Repetition function to repeat the string "a" six times.
a_vec <- rep(c("a"),times=6)
#Prints the output for easy viewing.
a_vec
```

2. `1 3 ... 99` *(the odd numbers)*

```{r}
# Creates a sequence starting at 1, ending at 99, and increasing by 2 everytime to ensure that
# only the odd numbers are in the sequence.
odd_num <- seq(1,99,by=2)
#Prints the vector
odd_num
```

3. `1 1 1 2 2 2 3 3 3`

```{r}
# These lines create respective vectors for each number using the repetition function.
one_vec <- rep(c(1),times=3)
two_vec <- rep(c(2),times=3)
three_vec <- rep(c(3),times=3)
# This line pastes all three together in a final vector, and then prints it.
final_vec <- c(paste(one_vec), paste(two_vec), paste(three_vec))
# Converts previous vector from string to numeric.
as.numeric(final_vec)

# Here is the same solution but a bit 'cleaner' but not the first way I thought about doing it.
final_vec1 <- c(rep(c(1),times=3), rep(c(2),times=3), rep(c(3),times=3))
final_vec1
```

## Problem 3 (Verzani problem 2.3)
*Let our small data set be* `2 5 4 10 8`.

1. *Enter this data into a data vector `x`.*

```{r}
# Vector name is 'x' as desired and the function 'c' which stands for concatenate will be used.
x <- c(2,5,4,10,8)
```

2. *Find the square of each number.*

```{r}
# The first line takes the square of each number and the second line prints the output of the new vector.
x^2
```

3. *Subtract 6 from each number.*

```{r}
# Subtracts 6 from every value in the vector 'x'.
x-6
```

4. *Subtract 9 from each number and then square the answer.*

```{r}
# Order of Operations is important here so it will subtract 9 from each value and
# then it will square the result and automatically print it.
(x-9)^2
```