---
title: "MATH 3070 Lab Project 13"
author: "Max Martin"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: true
  html_document:
    toc: true
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 9.14)
*The data set `normtemp` (**UsingR**) contains measurements of 130 healthy, randomly selected individuals. The variable `temperature` contains normal body temperature. Does the data appear to come from a Normal distribution? If so, perform a $t$-test to see if the commonly assumed value of 98.6 degrees fahrenheit is correct. (Studies have suggested that 98.2 degrees fahrenheit is more accurate.)*

```{r, tidy = TRUE}
# Load the required library
library(UsingR)
# Run the t-test using the mean of 98.6
t.test(normtemp$temperature, mu=98.6)
# The output p-value is incredibly small which signifies that the assumed value
# of 98.6 is not correct. However, when run with mu=98.2, the p-value is very
# large which would support that 98.2 degrees is the normal body temperature.
```

$\textcolor{red}{blue}$

## Problem 2 (Verzani problem 9.4)
*In the United States in 2007, the proportion of adults age 21-24 who had no medical insurance was 28.1 percent. A survey of 75 recent college graduates in this age range finds that 40 percent are without insurance. Does this support a difference from the nationwide proportion? Perform a test of significance and report the p-value. Is it significant? (Perform this test "by hand", not using `prop.test()`.)*

```{r, tidy = TRUE}
# Not-graded
```

## Problem 3 (Verzani problem 9.16)
*A one-sided, one-sample $t$-test will be performed. What sample size is needed to have a power of 0.80 for a significance level of 0.05 if `delta = 0.05` and the population standard deviation is assumed to be 5?*

```{r, tidy = TRUE}
# Code taken from lecture and then filled in with appropriate data.
power.t.test(power =.8, delta =0.05, sd =5, sig.level=.05, alternative="one.sided")
# We need to have a sample size of 123,652 to get the desired power level.
```

## Problem 4 (Verzani problem 9.31)
*For the `babies` (**UsingR**) data set, the variable `age` contains the recorded mom's age and `dage` contains the dad's age for several cases in the sample. Do a significance test of the null hypothesis of equal ages against a one-sided alternative that the dads are older in the sampled population.*

```{r, tidy = TRUE}
# Splits the data into mom and dad ages and then runs the t-test from lecture.
mom <- babies$age
dad <- babies$dage
t.test(mom, dad, alternative = "less", paired = TRUE)
# Because the p-value is super small, it signifies that this result is significant
# and that fathers are normally older than mothers.
```