---
title: "MATH 3070 Lab Project 7"
author: "Max Martin"
date: "October 17, 2024"
output:
  pdf_document:
    toc: true
  html_document:
    toc: true
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 5.6)
*For the `batting` (**UsingR**) data set, make parallel boxplots of the batting average (`H/AB`) for each team. Which team had the greatest median average? (Use **lattice** functions for this problem.)*

```{r, tidy=TRUE, error=TRUE}
# Importing libraries
library(UsingR)
library(lattice)
library(ggplot2)

#Box plot for each team, labels are hard to read unless the zoom feature
# is used but the highest average is from Anaheim (first entry at left).
bwplot(data=batting, H/AB ~ teamID)

```

## Problem 2 (Verzani problem 5.7)
*For the `mtcars` data set, produce graphics of the following using **ggplot2**:*

1. *Boxplots for miles per gallon (`mpg`) for groups defined by the number of gears (`gear`).*

```{r, tidy=TRUE, error=TRUE}
# Takes the dataset and plots a box and whiskey by mpg and then groups it by
# number of cylinders. Second line is the boxplot call.
ggplot(mtcars, aes(x=mpg, group =gear))+
  geom_boxplot()
```

3. *A scatterplot of `mpg` modeled by horsepower (`hp`). Create facets by the number of cylinders (`cyl`) and `gear`.*

```{r, tidy=TRUE, error=TRUE}
# Creates scatter plot based on the x,y variables as desired. Last line creates
# the 2d facet based on gear and cylinder.
ggplot(mtcars, aes(x=mpg, y=hp))+
  geom_point()+
  facet_grid(gear~cyl)
```

## Problem 3
*Using the `batting` data set (UsingR), create a visualization that does the following:*

* *Plots the* rate *of intentional walks (that is, the number of intentional walks divided by the number of times a player was at bat; these are the `IBB` and `AB` variables in the data set, respectively) against the* rate *of home runs (the `HR` variable in the data set) as a scatterplot*

* *Draws a trend line for these variables*

* *Identifies and labels the outlier in the data set in these variables (easily spotted once the scatter plot is drawn)*

*(Hint: `geom`-type functions can accept data arguments and will use the data set passed rather than the default for the chart. So for the third requirement, consider adding a text layer with `geom_text(data = ..., aes(...))` where the argument passed to `data` is a subset of the data set consisting of the outlier, and `aes(...)` defines how to label that outlier.)*

```{r, tidy = TRUE, error=TRUE}
# This finds the one row that contains the outlier.
max <- subset(batting, subset = IBB ==max(IBB))

# Creates plot based on x,y variables. Then creates a scatterplot. Third line
# creates a blue trend line. Last line takes the subset from above and labels
# it with the number of IBB and makes it red to stand out.
ggplot(batting, aes(x= IBB/AB, y=HR/AB))+
  geom_point()+
  geom_smooth(method=lm, se=FALSE, col='blue', size=1)+
  geom_text(data=max,aes(label= IBB, color='red',hjust=1.25,vjust=1))
```

