---
title: "MATH 3070 Lab Project 10"
author: "Max Martin"
date: "November 7,2024"
output:
  pdf_document:
    toc: true
  html_document:
    toc: true
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

*Since this assignment involves simulation, I set the seed to the following in order to get the same results:*

```{r}
set.seed(5292016)
```

## Problem 1 (Verzani problem 6.2)
*Roll a pair of dice. Let $X$ be the largest value shown on the two dice. Use `sample()` to simulate five values of $X$.*

```{r, echo=FALSE}
# This code block resets the random seed in order to get consistent results. This will be hidden in the final document, but YOU MUST NOT CHANGE THIS!
set.seed(5292016)
```

```{r, error=TRUE, tidy=TRUE}
# Does a random sample for two separate dice and then finds the maximum of
# those values and outputs them.
die_one <- sample(c(1,2,3,4,5,6), 5, replace = TRUE)
die_two <- sample(c(1,2,3,4,5,6), 5, replace = TRUE)

pmax(die_one, die_two)
```

## Problem 2 (Verzani problem 6.3)
*The National Basketball Association lottery to award the first pick in the draft is held by putting 1,000 balls into a hopper and selecting one. The teams with the worst records the previous year have a greater proportion of the balls. The data set `nba.draft` (**UsingR**) contains the ball allocation for the year 2002. Use `sample()` with Team as the data vector and `prob=Balls` to simulate the draft. What team do you select? Repeat until Golden State is chosen. How long did it take?*

```{r, echo=FALSE}
# This code block resets the random seed in order to get consistent results. This will be hidden in the final document, but YOU MUST NOT CHANGE THIS!
set.seed(5292016)
```

```{r, error=TRUE, tidy=TRUE}
# Loads the library we need
library(UsingR)
# Sample pulling from the team list, not replacing because once a team has been
# chosen, they can't be chosen again, and then the probability is defined as
# the ball allocation.
sample(nba.draft$Team, replace = FALSE, prob=nba.draft$Balls)
```

## Problem 3 (Verzani problem 6.23)
*Find the quintiles ($0^{\text{th}}$, $20^{\text{th}}$, $40^{\text{th}}$, $60^{\text{th}}$, $80^{\text{th}}$, and $100^{\text{th}}$ quantiles/percentiles) of the standard Normal distribution (this is a normal distribution with mean 0 and standard deviation 1).*

```{r, error=TRUE, tidy=TRUE}
# Creates a list from 0th Percentile to 100th Percentile
qnorm(c(0,.2,.4,.6,.8,1), mean=0, sd=1)
```
