---
title: "MATH 3070 Lab Project 4"
author: "Max Martin"
date: "September 8, 2016"
output:
  pdf_document:
    toc: true
  html_document:
    toc: true
---
4
*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 2.43)
*The `time` variable in the `nym.2002` data set (**UsingR**) contains the time to finish the 2002 New York City Marathon for a random sample of the finishers.*

1. *What percent ran the race in under 3 hours? (note that the data is in minutes)*

```{r}
library(UsingR)
# This line counts the number of finishers under 180 minutes (3 hours)
fast_finishers <- length(which(nym.2002$time < 180))
# Total finishers of the race
total_finishers <- length(nym.2002$time)
# Computes percentage of finishers under 3 hours
(fast_finishers/total_finishers)*100

```

2. *What is the time cutoff for the top 10%? The top 25%?*

```{r}
# Notice that these are the 10th and 25th percentiles, respectively
# First column gives the 10th percentile and the second column gives the 25th 
# percentile
quantile(nym.2002$time, c(.1, .25))
```

3. *What time cuts off the bottom 10%?*

```{r}
# Output is the 90th percentile which would show the cutoff for the bottom 10%.
quantile(nym.2002$time, c(.9))
```

## Problem 2 (Verzani problem 4.1)
*The data set `UScereal` (**MASS**) contains data on cereals sold in the United States in 1993. For this data set, answer the following questions using R (i.e. MUST answer questions using a code. Do not count by hand):*

1. *How many rows does the data frame have? Columns?*

```{r}
# This line gives the number of rows
nrow(UScereal)
# This line gives the number of columns
ncol(UScereal)
```

2. *How many different manufacturers are included?*

```{r}
# This counts the number of unique manufacturers in the table.
length(unique(UScereal$mfr))
```

3. *How many vitamin categories are included?*

```{r}
# This counts the number of unique vitamin categories.
length(unique(UScereal$vitamins))
```

4. *How many cereals have a sugar level above 10?*

```{r}
# This line counts all values in the sugar column greater than 10.
length(which(UScereal$sugars > 10))
```

5. *What is the mean calorie value for cereals with more than 5 grams of fat? Less than or equal to 5?*

```{r}
# The inside qualifier gives the calorie counts of the entries that have more 
# than 5 grams of fat and then the outside function just takes the mean of them.
mean(UScereal$calories[UScereal$fat > 5])
# This code is nearly identical except that it indexes the entries that have 
# less than 5 grams of fat.
mean(UScereal$calories[UScereal$fat <= 5])
```

6. *What is the mean calorie value for cereals on the middle shelf (2)?*

```{r}
# This in very similar to the previous code except that it indexes the entries 
# that are on the middle shelf.
mean(UScereal$calories[UScereal$shelf == 2])
```

## Problem 3
*Create a data frame containing the data in the following table:*

| First    | Last      | Age |
|----------|-----------|-----|
| Marcus   | Holstein  | 23  |
| Samuel   | Adams     | 56  |
| Gus      | McPherson | 43  |
| Margaret | Olsen     | 41  |
| Zim      | Newbold   | 95  |

```{r}
# I first created 3 separate vectors with the information and then combined them
# in a dataframe.
First <- c("Marcus", "Samuel", "Gus", "Margaret", "Zim")
Last <- c("Holstein", "Adams", "McPherson", "Olsen", "Newbold")
Age <- c(23, 56, 43, 41, 95)
names <- data.frame(First, Last, Age)
names
```
