---
title: "MATH 3070 Lab Project 8"
author: "Max Martin"
date: "October 24, 2024"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 3.2)
*For the `michelson` (**MASS**) data set, produce a density plot comparing `Speed` between Experiments 1 and 2.*

```{r, tidy=TRUE, error=TRUE}
# Your code here
library(MASS)
# Split data by experiment number
michelson_split<-split(michelson$Speed, michelson$Expt)
# Plots the density of the first experiment and inserts a limit on the
# y-axis so that the whole plot is visible
plot(density(michelson_split$"1"), col='red', ylim=c(0,0.006))
# Plots the density of the second experiment with a different color.
lines(density(michelson_split$"2"), col='blue')
```

## Problem 2 (Verzani problem 3.4)
*Three students record the time spent on homework per class. Their data is:*

| Student| 1  | 2  | 3  | 4  | 5 |
|:-------|---:|---:|---:|---:|--:|
| Marsha | 25 | 0  | 45 | 90 | 0 |
| Bill   | 30 | 30 | 30 | 30 |   |
| Holly  | 15 | 0  | 90 | 0  |   |

*Use a list to store these values. Then create a boxplot to compare. (You must use `boxplot()`'s formula interface for this problem.)*

```{r, tidy=TRUE, error=TRUE}
# Creates list given the data in the frame
hw_list <- list(
  Marsha = c(25,0,45,90,0),
  Bill = c(30,30,30,30),
  Holly = c(15,0,90,0)
)
# Creates boxplot based on the list
boxplot(hw_list)
```

## Problem 3 (Verzani problem 3.5)
*A group of nursing students take turns measuring some basic assessments. Their data is:*

|          | Temp | Pulse | Systolic | Diastolic |
|----------|------|-------|----------|-----------|
| Jackie   | 98.2 | 96    |  134     | 90        |
| Florence | 98.6 | 56    |  120     | 80        |
| Mildred  | 98.2 | 76    |  150     | 95        |

*Create a data frame of these values. Will `plot()` and `boxplot()` produce the same graphic?*

```{r, tidy=TRUE, error=TRUE}
# Creates data frame from the information in the table above.
nursing_data <- data.frame(
  Names = c("Jackie", "Florence", "Mildred"),
  Temp = c(98.2,98.6,98.2),
  Pulse = c(96,56,76),
  Systolic = c(134,120,150),
  Diastolic = c(90,80,95)
)
# Creates a boxplot of the different values.
boxplot(nursing_data[,-1])
# Creates a plot from the data. Creates numerous different plots.
plot(nursing_data)

# These graphs are not the same. The boxplot creates a box plot (obviously)
# but the plot creates numerous graphs of different x and y values on the axis
# as we discussed a few weeks ago.
```

## Problem 4 (Verzani problem 3.8)
*The second argument to `split` can be a list of factors. The result is that all interactions (possible combinations) are used for the groups. In the `ToothGrowth` data set, growth (`len`) is measured for two types of supplements (`supp`) and three doses (`dose`). Split this `len` value into 6 groups.*

```{r, tidy=TRUE, error=TRUE}
# Double split in one line. Splits based on the supplement and the dose so that
# the output tells you the length by a specific supplemement and dose.
split(ToothGrowth$len, list(ToothGrowth$supp,ToothGrowth$dose))

```