---
title: "MATH 3070 Lab Project 5"
author: "Max Martin"
date: "September 20, 2018"
output:
  pdf_document:
    toc: true
  html_document:
    toc: true
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***


## Problem 1 (Verzani problem 4.7)
*Use the `subset()` function to return a data frame made from the `Cars93` (**MASS**) data frame consisting only of `non-USA` cars in origin, with 4 cylinders and a maximum price of \$15,000 or less.*

```{r, tidy=TRUE,error=TRUE}
# Importing the library we need.
library(UsingR)
# Calling the subset function and I am iterating for all the foreign cars that
# have 4 cylinders and  maximum price of less than $15k.
subset(Cars93, subset = Origin == 'non-USA' & Cylinders == 4 & Max.Price <= 15.0)
```

## Problem 2 (Verzani problem 4.10)
*Find the standard deviation of each variable in the `mtcars` data set.*

```{r, tidy=TRUE, error=TRUE}
# I am using the 'sapply' function to call the data set I want and then calling
# the standard deviation function.
sapply(mtcars, sd)
```

## Problem 3 (Verzani problem 4.11)
*Find the standard deviation for each numeric variable in `Cars93` (**MASS**).*

```{r, tidy=TRUE, error=TRUE}
# The first line takes all of the columns that have numeric variables and then
# the second line uses the sapply similarily to Problem 2 to take the standard
# deviation of all the numeric variables.
Cars93_num <- subset(Cars93, select = sapply(Cars93, is.numeric))
sapply(Cars93_num, sd)
```

## Problem 4
*You can find data describing various statistics on 2012 Olympic participating nations such as population and medal counts in the comma-separated value file (olympic-medals2012.csv). Load this dataset into R in a data frame and do the following:*

1. *Create a new data frame containing only the country's ISO code (a three-letter code for the country; USA is the United States of America, and DZA Algeria), name, population, and counts for gold, silver, and bronze. This data frame should be called `olympic2012`.*

```{r, tidy=TRUE, error=TRUE}
# The first line reads the csv file into a new variable that I have assigned.
oly_data <- read.csv("olympic-medals2012.csv")
# This line only prints the desired columns by using the subset function.
olympic2012 <- subset(oly_data, select = c(ISO, Country.name, pop.2010, Gold, Silver, Bronze))
olympic2012
```

2. *What proportion of countries earned no medals? Answer this using `olympic2012`.*

```{r, tidy=TRUE, error=TRUE}
# This line counts the number of rows of the subset of 'olympic2012' of countries
# that did not win any medals.
zero_medals <- nrow(subset(olympic2012, subset = Gold==0 & Silver==0 & Bronze==0))
# This line counts the number of rows in the entire 'olympic2012' dataset, so the
# total number of countries.
total_countries <- nrow(olympic2012)
# This line finds the percentage of countries that did not win any medals.
(zero_medals/total_countries)*100
```

