---
title: "MATH 3070 Lab Project 6"
author: "Max Martin"
date: "October 3, 2024"
output:
  pdf_document:
    toc: true
  html_document:
    toc: true
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 5.1)
*For the `UScereal` (**MASS**) data set, create a scatter plot of `calories` modeled by `sugars` using the `shelf` variable to create different plot characters. Add a legend to indicate the shelf number. Is there any patterns? (Use base R plotting for this problem.)*

```{r, tidy=TRUE, error=TRUE}
library(MASS)
#Your code here
with(UScereal,
# First, the scatter plot
plot(calories, sugars,
# Different colors for different shelves
col = as.numeric(shelf),
# Different characters for different shelves
pch = as.numeric(shelf),
# Axis labels and plot table
xlab = "Calories", ylab = "Sugar", main = "Relationship between Calories and Sugar"
)
)
legend(400, 8, c("1", "2", "3"), col = 1:3, pch = 1:3)

# The pattern is that in general the more calories, the more sugar the cereal has.
```

## Problem 2 (Verzani problem 5.3)
*For the data set `UScereal` (**MASS**) make a pairs plot of the numeric variables. Which correlation looks larger: fat and calories or fat and sugars?*

```{r, tidy=TRUE, error=TRUE}
# Creates scatter plots between all the numeric variables. Shelf is not included because while
# it is a number, it is being used as a classification in the data set.
pairs(UScereal[c("calories", "protein", "fat", "sodium", "fibre", "carbo", "sugars", "potassium")])

# Fat and calories has a larger correlation based on the eyeball test.
```

## Problem 3 (Verzani problem 5.4)
*For the data set `batting` (**UsingR**) make a bubble plot of home runs hit (`HR`) modeled by hits (`H`) where the scale factor for each point is given by `sqrt(SO)/10`. Is there any story to be told by the size of the points? (You must use base R plotting for this problem.)*

```{r, tidy=TRUE, error=TRUE}
library(UsingR)
# Plots HRs against hits from the dataset 'batting'
plot(HR ~ H, data = batting,
# filled circles
pch = 16,
# Changed the color to a light gray because I think it is easier to view.
col=rgb(red = 0, green = 0, blue = 0, alpha = 0.250),
# Size of the points dependent on the square root of strikeouts divided by 10.
cex = sqrt(SO)/10)

# The size of the points says whether or not the player struck out more.
# Based on the graph I would conclude that players with more hits and HRs
# also struck out more based on the size of the dots.
```

